YouTube Kids: The Effect of YouTube on Children’s Racial Learning

### 2025-03-08 manuscript.qmd
updated references
updated final qmd draft

library(svglite)
library(papaja)
library(knitr)
library(broom)
library(tidyverse)

@@

## Introduction

@@

## Methods {#sec-methods}

### Participants and Procedures {#sec-participants-and-procedures}
This study will include children between the ages of 8 and 13. Though children may express negative racial attitudes prior to this point in development, during early adolescence, children develop the ability to recognize and reflect on the racial patterns and dynamics present in their environments (Hughes & Watford, 2022). As such, this age range should allow me to observe how the observation racial regularities present on YouTube may affect children’s stereotyping and prejudicial attitudes, and how such a phenomenon develops. Participants will be recruited through Qualtrics Panels, which will allow me to obtain a representative sample of parents and children; other studies have used Qualtrics Panels with similar methods and populations (Byrd & Ahn, 2020).

Data will be collected during February and March of 2025 from families recruited via Qualtrics Panels. Participating families will receive two Qualtrics surveys to be completed asynchronously, and they will receive compensation (around $10-$15; the final amount will be determined by Qualtrics Panels) after both surveys have been completed. First, parents will complete a demographics and YouTube usage survey, in which they will answer questions related to parent and child demographics (child age, race/ethnicity, parent income and level of education, etc), as well as questions regarding their child’s YouTube usage (for instance, time spent on YouTube, as reported by their child’s device screen time). 
Then, children will complete their own survey.

### Measures {#sec-measures}
First, they will answer questions related to their YouTube usage (perceptions of time spent). Next, they will either answer more questions pertaining to YouTube content, or their general racial attitudes; either block of questions will appear randomly, so as to reduce the influence of question order. In the racial attitudes section, children will answer questions regarding outgroup prejudices, as rated on a Likert scale. They will also complete one friend choice item, as a simple exploratory measure of racial preference. In the YouTube content section, children will be asked to think of their favorite YouTuber as they answer questions related to whether they have a parasocial relationship with that YouTuber, as well as their observations of racial regularities on YouTube.

## Results {#sec-results}

@@

  return(report)

}

@@

# References

>>>>

library(svglite)
library(papaja)
library(knitr)
library(broom)
library(kableExtra)
library(psych)
library(tidyverse)

@@

@@

# Methods {#sec-methods}

### Participants and Procedures {#sec-participants-and-procedures}
This study includes dyads of parents and children between the ages of 8 and 13 [^1]. Though children may express negative racial attitudes prior to this point in development, during early adolescence, children develop the ability to recognize and reflect on the racial patterns and dynamics present in their environments [@hugheswatford_2022_racial]. As such, this age range allows me to observe how the observation racial regularities present on YouTube may affect children’s stereotyping and prejudicial attitudes, and how such a phenomenon develops. Participants were recruited through Qualtrics Panels, allowing me to obtain a representative sample of parents and children; other studies have used Qualtrics Panels with similar methods and populations [@byrdahn_2020_profiles].

[^1]: Pilot data has demonstrated that Qualtrics Panels has not, thus far, been as stringent in participant age verification. As such, data used presently is from a broader age range than will be included in the final sample, after stricter age validation has been included.

Pilot data has been collected in March of 2025 from families recruited via Qualtrics Panels (*N* = `r length(transaction_id)`). Participating families receive two Qualtrics surveys to be completed asynchronously, and receive compensation (as determined by Qualtrics Panels) after both surveys have been completed. First, parents complete a demographics and YouTube usage survey, then children complete their own survey.

### Measures {#sec-measures}

In the parent survey, participants answer questions related to parent and child demographics (child age, race/ethnicity, parent income and level of education, etc), as well as questions regarding their child’s YouTube usage (for instance, time spent on YouTube, as reported by their child’s device screen time).

In the child survey, children answer questions related to their YouTube usage, such as time spent on YouTube and their favorite genre. 
Next, they will either answer more questions pertaining to YouTube content, or their general racial attitudes; either block of questions will appear randomly, so as to reduce the influence of question order. In the racial attitudes section, children will answer questions regarding outgroup prejudices, as rated on a Likert scale. They will also complete one friend choice item, as a simple exploratory measure of racial preference. In the YouTube content section, children will be asked to think of their favorite YouTuber as they answer questions related to whether they have a parasocial relationship with that YouTuber, as well as their observations of racial regularities on YouTube.

```{r}
#| label: report-reliability-function
#| echo: false
#| message: false
#| warning: false

alpha(youtube %>% select(malleable_1:malleable_4))
alpha(youtube %>% select(homophily_appear_1:homophily_appear_5))
alpha(youtube %>% select(homophily_behave_1:homophily_behave_6))
alpha(youtube %>% select(parasocial_1:parasocial_5))
alpha(youtube %>% select(regularities_1:regularities_5))

return_alpha <- function(data, cols) {
  # select data 
  selected_data <- data %>% select({{ cols }})
  # compute alpha
  alpha_result <- psych::alpha(selected_data, check.keys = TRUE)
  # Extract and return the raw alpha value
  return(alpha_result$total$raw_alpha)
}

reliability <- 
  return_alpha(malleable_1:malleable_4) 
```

```{r}
#| label: tbl-reliability
#| tbl-cap: "Reliability of each scale used"
#| echo: false
#| message: false
#| warning: false

# Generate kable table
kable(reliability, format = "html", caption = "Function Outputs in One Column") %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

# Results {#sec-results}

@@

  return(report)    
}

@@

```
# Discussion

\clearpage
# References
:::{refs}
:::
